Flexibility of interactions depends on habitat suitability

### 2019-08-17 paper/manuscript.Rmd
Some extra refs

We then used a series of bayesian multilevel models to evaluate the impact of environmental suitability on the number of interacting species. 
These models differed on the predictors included and allowed us to evaluate the relative importance of suitability. 
Our response variable was the number of species it interacts with in a community, the species degree. 
We modelled degree using a logarithmic link function and a Poisson distribution. 
Nevertheless results were qualitatively the same if instead we model the normalised degree (REF Martin Gonzalez 2010) using a binomial distribution in which degree is the number of successes and the number of species in the opposite guild is the number of trials (Supp info).

>>>>

We then used a series of bayesian multilevel models to evaluate the impact of environmental suitability on the number of interacting species. 
These models differed on the predictors included and allowed us to evaluate the relative importance of suitability. 
Our response variable was the number of species it interacts with in a community, the species degree. 
We modelled degree using a logarithmic link function and a Poisson distribution. 
Nevertheless results were qualitatively the same if instead we model the normalised degree [@martin_gonzalez_centrality_2010] using a binomial distribution in which degree is the number of successes and the number of species in the opposite guild is the number of trials (Supp info).
